Understanding missing diffraction reflections

### 2018-03-06 Ben_Manuscripts/structure_paper/diffraction.tex
updates

Initial configurations are built in two ways: Parallel displaced and Sandwiched
(Figure ~\ref{fig:initial_configs}).  The simulated diffraction patterns for
equilibrated systems started in each configuration at 300 K are shown in Figure
~\ref{fig:xrd}. We observe stronger features in the alkane chain region when
the temperature is lowered to 280K (Figure~\ref{fig:xrd_280}). At both
temperatures we are missing what appears to be a subharmonic located at
($q_r=0$,$q_z=0.85$) in the experimental pattern. We would like to know 
why it doesn't appear -- whether it has something to do with our system
or the math behind the simulated structure factor itself.

\begin{figure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwichedlayers.png}
                \caption{Sandwiched}\label{fig:sandwichedlayers}
        \end{subfigure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offsetlayers.png}
                \caption{Parallel Displaced}\label{fig:offsetlayers}
        \end{subfigure}
	\caption{}\label{fig:initial_configs}
\end{figure}

\begin{figure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{rzplot_layered_300K.png}
                \caption{Sandwiched}\label{fig:xrd_layered}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{rzplot_offset_300K.png}
                \caption{Parallel Displaced}\label{fig:xrd_offset}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{WAXS_raw.png}
                \caption{Experiment}\label{fig:xrd_exp}
        \end{subfigure}
	\caption{}\label{fig:xrd}
\end{figure}

\begin{figure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{layered_rzplot.png}
                \caption{Sandwiched}\label{fig:xrd_layered}
        \end{subfigure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offset_rzplot.png}
                \caption{Parallel Displaced}\label{fig:xrd_offset}
        \end{subfigure}
	\caption{}\label{fig:xrd_280}
\end{figure}

The hypothesis is that the subharmonic appears due to the reflection located at
($q_r=0,q_z$=1.7) in the experimental pattern. This reflection likely appears
because aromatic rings of monomer head groups pi-stack on top of each other
3.7~\AA apart. The subharmonic does not appear in our simulated patterns and
we need a good explanation for why that is the case. I explored fourier
transforms in various dimensions to help increase my understanding.

@@

\begin{figure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_highres.png}
                \caption{Real space - high resolution}\label{fig:real_delta_1d_highres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_medres.png}
                \caption{Real space - medium resolution}\label{fig:real_delta_1d_medres}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_lowres.png}
                \caption{Real space - low resolution}\label{fig:real_delta_1d_lowres}
	\end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_highres.png}
                \caption{Fourier space - high resolution}\label{fourier_delta_1d_highres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_medres}
                \caption{Fourier space - medium resolution}\label{fourier_delta_1d_medres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_lowres}
                \caption{Fourier space - low resolution}\label{fourier_delta_1d_lowres}
        \end{subfigure}
	\caption{Less subharmonics are present as resolution decreases}\label{fig:1D_deltas}
\end{figure}

@@

\begin{figure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_highsig.png}
                \caption{Real space - sigma = 1}\label{fig:real_gauss_1d_highsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_medsig.png}
                \caption{Real space - sigma = 0.1}\label{fig:real_gauss_1d_medsig}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_lowsig.png}
                \caption{Real space - sigma = 0.001}\label{fig:real_gauss_1d_lowsig}
	\end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_highsig.png}
                \caption{Fourier space - sigma = 1}\label{fourier_gauss_1d_highsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_medsig}
                \caption{Fourier space - sigma = 0.1}\label{fourier_gauss_1d_medsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_lowsig}
                \caption{Fourier space - sigma = 0.001}\label{fourier_gauss_1d_lowsig}
        \end{subfigure}
	\caption{Using high real space resolution (same as Figure~\ref{1D_deltas}), it
                 is evident that a smaller sigma leads to more subharmonics. As sigma
		 approaches zero, the behavior is the fourier transform resembles that
		 of delta functions. Otherwise, the fourier transform of a gaussian is
		 a gaussian.}\label{fig:1D_gauss_sigma}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.45\textwidth}
	        \centering
                \includegraphics[width=\textwidth]{real_2d_1column.png}
                \caption{Real space - $\sigma_x=\sigma_y$ = 0.001}\label{fig:real_2d_1column}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_2column.png}
                \caption{Real space - $\sigma_x=\sigma_y$ = 0.001}\label{fig:real_2d_2column}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_1column.png}
                \caption{Fourier space}\label{fig:fourier_2d_1column}
	\end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_2column.png}
                \caption{Fourier space}\label{fourier_2d_2column}
        \end{subfigure}
	\caption{A single column of equispaced scatterers shows up as horizontal lines
		 with spacing equal to the inverse of the distance between scatters. Adding
		 a second column (b) causes the horizontal lines to become dots spaced apart
		 by the inverse of the distance between columns. Adding more columns would
                 follow the same trend.}~\label{fig:2d_columns_simple}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_74_1column.png}
                \caption{Real space - $\sigma_x$=$\sigma_y$=0.1}\label{fig:real_2d_74_1column}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_74_1column.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_74_1column_highysig.png}
                \caption{Real space - $\sigma_x$=0.1, $\sigma_y$=0.4}\label{fig:real_2d_74_1column_highysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_74_1column_highysig.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column_highysig}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_1column_74_highxysig.png}
                \caption{Real space - $\sigma_x$=0.4, $\sigma_y$=0.4}\label{fig:real_2d_1column_75_highxysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_1column_74_highxysig.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column_highxysig}
        \end{subfigure}

        \caption{A single column of scatterers spaced 7.4 \AA apart shows up as horizontal lines
                 with spacing equal to the inverse of the distance between scatters. One of the
                 subharmonics corresponds to a real spacing distance of 3.7 \AA. If we adjust the 
	         sigmas of the scattering, we can change the relative intensity of each
                 horizontal line in fourier space.}~\label{fig:2d_columns_offset}
\end{figure}

>>>>

Initial configurations are built in two ways: Parallel displaced and Sandwiched
(Figure ~\ref{fig:initial_configs}).  The simulated diffraction patterns for
equilibrated systems started in each configuration at 300 K are shown in Figure
~\ref{fig:xrd}. We observe stronger features in the alkane chain region when
the temperature is lowered to 280K (Figure~\ref{fig:xrd_280}). At both
temperatures we are missing what appears to be a subharmonic located at
($q_r=0$, $q_z=0.85$) in the experimental pattern. We would like to know 
why it doesn't appear -- whether it has something to do with our system
or the math behind the simulated structure factor itself.

\begin{figure}[h]
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwichedlayers.png}
                \caption{Sandwiched}\label{fig:sandwichedlayers}
        \end{subfigure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offsetlayers.png}
                \caption{Parallel Displaced}\label{fig:offsetlayers}
        \end{subfigure}
	\caption{}\label{fig:initial_configs}
\end{figure}

\begin{figure}[h]
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{rzplot_layered_300K.png}
                \caption{Sandwiched}\label{fig:xrd_layered}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{rzplot_offset_300K.png}
                \caption{Parallel Displaced}\label{fig:xrd_offset}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{WAXS_raw.png}
                \caption{Experiment}\label{fig:xrd_exp}
        \end{subfigure}
	\caption{}\label{fig:xrd}
\end{figure}

\begin{figure}[h]
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{layered_rzplot.png}
                \caption{Sandwiched}\label{fig:xrd_layered}
        \end{subfigure}
        \begin{subfigure}{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offset_rzplot.png}
                \caption{Parallel Displaced}\label{fig:xrd_offset}
        \end{subfigure}
	\caption{}\label{fig:xrd_280}
\end{figure}

The hypothesis is that the subharmonic appears due to the reflection located at
($q_r=0, q_z$=1.7) in the experimental pattern. This reflection likely appears
because aromatic rings of monomer head groups pi-stack on top of each other
3.7~\AA apart. The subharmonic does not appear in our simulated patterns and
we need a good explanation for why that is the case. I explored fourier
transforms in various dimensions to help increase my understanding.

@@

\begin{figure}[h]
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_highres.png}
                \caption{Real space - high resolution}\label{fig:real_delta_1d_highres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_medres.png}
                \caption{Real space - medium resolution}\label{fig:real_delta_1d_medres}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_delta_1d_lowres.png}
                \caption{Real space - low resolution}\label{fig:real_delta_1d_lowres}
	\end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_highres.png}
                \caption{Fourier space - high resolution}\label{fourier_delta_1d_highres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_medres}
                \caption{Fourier space - medium resolution}\label{fourier_delta_1d_medres}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_delta_1d_lowres}
                \caption{Fourier space - low resolution}\label{fourier_delta_1d_lowres}
        \end{subfigure}
	\caption{Less subharmonics are present as resolution decreases}\label{fig:1D_deltas}
\end{figure}

@@

\begin{figure}[h]
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_highsig.png}
                \caption{Real space - sigma = 1}\label{fig:real_gauss_1d_highsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_medsig.png}
                \caption{Real space - sigma = 0.1}\label{fig:real_gauss_1d_medsig}
        \end{subfigure}
	\begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_gauss_1d_lowsig.png}
                \caption{Real space - sigma = 0.001}\label{fig:real_gauss_1d_lowsig}
	\end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_highsig.png}
                \caption{Fourier space - sigma = 1}\label{fourier_gauss_1d_highsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_medsig}
                \caption{Fourier space - sigma = 0.1}\label{fourier_gauss_1d_medsig}
        \end{subfigure}
        \begin{subfigure}{0.33\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_gauss_1d_lowsig}
                \caption{Fourier space - sigma = 0.001}\label{fourier_gauss_1d_lowsig}
        \end{subfigure}
	\caption{Using high real space resolution (same as Figure~\ref{1D_deltas}), it
                 is evident that a smaller sigma leads to more subharmonics. As sigma
		 approaches zero, the behavior is the fourier transform resembles that
		 of delta functions. Otherwise, the fourier transform of a gaussian is
		 a gaussian.}\label{fig:1D_gauss_sigma}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{0.45\textwidth}
	        \centering
                \includegraphics[width=\textwidth]{real_2d_1column.png}
                \caption{Real space - $\sigma_x=\sigma_y$ = 0.001}\label{fig:real_2d_1column}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_2column.png}
                \caption{Real space - $\sigma_x=\sigma_y$ = 0.001}\label{fig:real_2d_2column}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_1column.png}
                \caption{Fourier space}\label{fig:fourier_2d_1column}
	\end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_2column.png}
                \caption{Fourier space}\label{fourier_2d_2column}
        \end{subfigure}
	\caption{A single column of equispaced scatterers shows up as horizontal lines
		 with spacing equal to the inverse of the distance between scatters. Adding
		 a second column (b) causes the horizontal lines to become dots spaced apart
		 by the inverse of the distance between columns. Adding more columns would
                 follow the same trend.}~\label{fig:2d_columns_simple}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_74_1column.png}
                \caption{Real space - $\sigma_x$=$\sigma_y$=0.1}\label{fig:real_2d_74_1column}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_74_1column.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_74_1column_highysig.png}
                \caption{Real space - $\sigma_x$=0.1, $\sigma_y$=0.4}\label{fig:real_2d_74_1column_highysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_74_1column_highysig.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column_highysig}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_2d_1column_74_highxysig.png}
                \caption{Real space - $\sigma_x$=0.4, $\sigma_y$=0.4}\label{fig:real_2d_1column_75_highxysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_2d_1column_74_highxysig.png}
                \caption{Fourier space}\label{fig:fourier_2d_74_1column_highxysig}
        \end{subfigure}
        \caption{A single column of scatterers spaced 7.4 \AA apart shows up as horizontal lines
                 with spacing equal to the inverse of the distance between scatters. One of the
                 subharmonics corresponds to a real spacing distance of 3.7 \AA. If we adjust the 
	         sigmas of the scattering, we can change the relative intensity of each
                 horizontal line in fourier space.}~\label{fig:2d_columns_offset}
\end{figure}

And now I move into 3D. The only difference in its calculation is that I use
\texttt{numpy.fft.fftn} instead of the 2D version. I come to the same
conclusion as in the 2D case. Lines appear that are spaced apart by a distance
equal to the inverse of the distance between points in the z direction
(Figure~\ref{fig:fourier_3d_lowdig}).  If there is disorder in the z-direction
(high $\sigma$) then lines at low z frequency fade
(Figure~\ref{fig:fourier_3d_highzsig}). If there is disorder in the x (or y)
direction, then intensity at low x frequencies fade
(Figure~\ref{fig:fourier_3d_highysig}).

\begin{figure}[h]
	\centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_3d_lowsig.png}
                \caption{Real space - $\sigma_z$=$\sigma_x$=$\sigma_y$=0.001}\label{fig:real_3d_lowsig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_3d_lowsig.png}
                \caption{Fourier space}\label{fig:fourier_3d_lowsig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_3d_highzsig.png}
                \caption{Real space - $\sigma_z$=0.5, $\sigma_x$=$sigma_y$=0.001}\label{fig:real_3d_highzsig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_3d_highzsig.png}
                \caption{Fourier space}\label{fig:fourier_3d_highzsig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_3d_highysig.png}
                \caption{Real space - $\sigma_z$=$sigma_y$=0.001, $\sigma_x$=0.5}\label{fig:real_3d_highysig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_3d_highysig.png}
                \caption{Fourier space}\label{fig:fourier_3d_highysig}
        \end{subfigure}
        \caption{A single column of scatterers spaced 7.4 \AA apart in 3D space shows up as horizontal lines
                 with spacing equal to the inverse of the distance between scatters. One of the
                 subharmonics corresponds to a real spacing distance of 3.7 \AA. If we adjust the
                 sigmas of the scattering, we can change the relative intensity of each
                 horizontal line in fourier space.}~\label{fig:3d_simple}
\end{figure}

The patterns are interesting, but they still don't fully explain the features.
The main problem is that the lines fade starting from the center (0 frequency)
of the fourier transform. They are quite strong at high frequency and very low
at zero. We see the opposite in the experimental pattern.

To address the problem, we need to make a more complicated system. So I'll
start by adding more columns and packing them hexagonally
(Figure~\ref{fig:hex_simple}). The dots of the dashed lines in the fourier
transform (Figure~\ref{fig:fourier_3d_hex_lowsig}) are spaced apart by the
inverse of distance between columns. If we add some uncertainty to the 
locations of the points in the columns, we see fading of low frequencies
as before. Interestingly, the pattern at x=0 does not fade despite the 
x/y uncertainties being as high as in Figure~\ref{fig:fourier_3d_highysig}. 
I'd need to do more to verify this, but it appears that the center does
not fade in the x direction as long as the uncertainty in the xy directions
is larger than the z direction.

\begin{figure}[h]
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_3d_lowsig.png}
                \caption{Real space - $\sigma_z$=$\sigma_x$=$\sigma_y$=0.001}\label{fig:real_3d_hex_lowsig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_3d_hex_lowsig.png}
                \caption{Fourier space}\label{fig:fourier_3d_hex_lowsig}
        \end{subfigure}
	\begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{real_3d_hex_highsig.png}
                \caption{Real space - $\sigma_x$=$sigma_z$=0.5, $\sigma_z$=0.8}\label{fig:real_3d_hex_highsig}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{fourier_3d_hex_highsig.png}
                \caption{Fourier space}\label{fig:fourier_3d_hex_highsig}
        \end{subfigure}

	\caption{}\label{fig:hex_simple}
\end{figure}

The original problem still persists after putting in more columns. That is, the
intensity of the horizontal lines at high frequencies is never lower than the
value at low frequency. Angle averaging helps resolve this
(Figure~\ref{fig:fourier_hex_angle_average}). With a little parameter tweaking,
it looks even better (Figure~\ref{fig:fourier_hex_angle_average_better}). There 
are still some high intensity areas at high frequency values. It is possible 
those would go away in more complicated systems.

\begin{figure}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{fourier_hex_angle_average.png}
		\caption{Fourier space - $\sigma_x$=$\sigma_z$=0.5, $\sigma_z$=0.8}\label{fig:fourier_hex_angle_average}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{fourier_hex_angle_average_better.png}
		\caption{Fourier space - $\sigma_x$=$\sigma_z$=0.5, $\sigma_z$=0.8}\label{fig:fourier_hex_angle_average_better}
	\end{subfigure}

	\caption{Angle averaging the same pattern shown in Figure~\ref{fig:fourier_3d_hex_highsig} 
	yields a pattern with the highest intensity concentrated at the center.}\label{fig:angle_averaged}
\end{figure}
